Your Awesome Title

### 2017-09-25 Doc/ms.Rmd
line space can be set in the yaml

---
title: "Your Awesome Title"
author: "Author One and Author Two"
date: '`r format(Sys.time())`'
output:
  bookdown::pdf_document2:
    includes:
      before_body: ../template/doc_prefix.tex
      in_header: ../template/preamble.tex
    keep_tex: yes
    latex_engine: pdflatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2: null
fontsize: 12pt
link-citations: yes
csl: ../template/oikos.csl
bibliography: ../template/ref.bib
---

>>>>

---
title: "Your Awesome Title"
author: "Author One and Author Two"
date: '`r format(Sys.time())`'
output:
  bookdown::pdf_document2:
    includes:
      before_body: ../template/doc_prefix.tex
      in_header: ../template/preamble.tex
    keep_tex: yes
    latex_engine: pdflatex
    number_sections: no
    toc: no
  bookdown::html_document2:
    number_sections: no
    theme: readable
    toc: yes
  bookdown::tufte_html2:
    number_sections: no
    toc: yes
  bookdown::word_document2: null
fontsize: 12pt
linestretch: 1.5
link-citations: yes
csl: ../template/oikos.csl
bibliography: ../template/ref.bib
---
